% Cies Resume/CV Template
% Cies Breijs (cies@kde.nl)
% https://github.com/cies/resume
% License: CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)

% Document Imports, etc.
\documentclass[10pt,a4paper]{article}
\include{structure}
\addbibresource{publications}

% Hyphenations
\hyphenation{Phylogenetic}

%-----------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%-----------------------------------------------------------------------------------

\begin{document} 

\maintitle{Alexander Safatli}{July 13, 1990}

\noindent\href{mailto:asafatli@dal.ca}{asafatli@dal.ca}\bull
\textsmaller{+}1 (902) 229-0408\bull \textbf{GitHub} \href{https://github.com/AlexSafatli/}{AlexSafatli}\bull
\textbf{LinkedIn} \href{http://ca.linkedin.com/in/asafatli}{asafatli}\\
100 Birch Tree Ln, B3R2N8\bull Halifax\bull Nova Scotia\bull Canada

\spacedhrule{0.9em}{-0.4em} % <hr />

%-----------------------------------------------------------------------------------
%	SUMMARY SECTION
%-----------------------------------------------------------------------------------

\roottitle{Summary}
\vspace{-1.3em}

\begin{multicols}{2}

\noindent \textit{I am currently a graduate student at Dalhousie University who is in his last term of studies towards a Master of Computer Science. My thesis topic is associated with a problem in the field of biology. Despite this, I see myself not as someone who specializes in that topic, but as someone who uses that topic to specialize in methodologies of computer science.}\\

I have taken numerous courses in different fields and topics of Computer Science, both at an undergraduate and graduate level, and have been the teaching assistant for a diverse a set of computer science courses. 

While I have no work experience outside of a commercial and university environment, I am incredibly prepared to learn and adapt to new software, languages, and tools. As to my areas of interest, I aspire to design, build, and explore complex computer models, for any application area, to perform tasks of significance. Furthermore, I stress that I am a devout in good quality products as well as a firm believer in loyalty.

\end{multicols}

\spacedhrule{0.5em}{-0.4em} % <hr />

%----------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------

\roottitle{Education}

\headedsection{Dalhousie University}{\textsc{Halifax, Canada}} {

\headedsubsection{Master of Computer Science}{Jan '14 -- Apr '15}
{\bodytext{Continued education in Advanced Data Structures, Algorithms, Heuristics, and Natural Language Processing. Written a thesis \textit{Sampling Discrete Combinatorial Spaces in Phylogenetics} that explores a combinatorial space problem found in the field of bioinformatics. A visualization and exploration of the space and relevant heuristics are carried out. \textit{Supervised} by Assoc. Prof. \href{mailto:cblouin@cs.dal.ca}{Christian Blouin}. \textit{Extracurricular}. Computer Science Graduate Society, Executive Secretary for later term of 2014.}}

\headedsubsection{Bachelor of Computer Science with Distinction \bull GPA 3.8 \bull Dean's List}{2008 -- 2013}
{\bodytext{Focused on advanced concepts in mathematics (incl. geometry, cryptography, linear algebra) alongside a strong understanding of chemistry, biology, and philosophy. The degree also featured experience working with clients inside the community through a Community Outreach program. \textit{Extracurricular}. Computer Science Society, Dalhousie University, Executive Secretary as of 2012-2013; Sodales Debating Society, Dalhousie University, Executive Secretary in 2010.}}}

\spacedhrule{0.5em}{-0.4em} % <hr />

%----------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------

\roottitle{Experience}


\headedsection{Dalhousie University}{\textsc{Halifax, Canada}}{

\headedsubsection
{Teaching Assistantship, Assist. Prof. \href{mailto:mcallist@cs.dal.ca}{Michael McAllister}}{Winter 2015}
{\bodytext{Helped mark written and programming assignments, alongside a number of other teaching assistants, for a class of around 100 students in the third-year undergraduate-level \textit{Operating Systems} course.}}

\headedsubsection
{Teaching Assistantship, Assoc. Prof. \href{mailto:cblouin@cs.dal.ca}{Christian Blouin}}{2012 -- 2014}
{\bodytext{Helped instruct classes of around 100 students and marked essays and examinations for \textit{Concepts in Computing} and \textit{Applications in Computing} first-year undergraduate courses. Also helped instruct and mark assignments for a smaller graduate-level course in concepts found in \textit{Bioinformatics}.}}

\headedsubsection
{Teaching Assistantship, Prof. \href{mailto:pcox@cs.dal.ca}{Philip T. Cox}}{Apr '14 -- Sep '14}
{\bodytext{Helped mark assignments and examinations, alongside another teaching assistant, for the \textit{Principles of Programming Languages} third-year undergraduate-level course.}}

\headedsubsection
{Research Assistant \& Software Developer, \href{http://web.cs.dal.ca/~cblouin/}{Blouin Lab}}
{2012 -- 2014}
{\bodytext{Orchestrated work in different areas of bioinformatics. Helped construct software libraries for geometric morphometric analysis of 2D and 3D biological structures, for molecular dynamics, for protein homology modelling, and for the parsing of essential file formats. Performed a great deal of debugging and restructuring of existing code base.}}

\headedsubsection
{Teaching Assistantship, Instr. \href{mailto:jfleming@cs.dal.ca}{James Fleming}}{2012 -- 2013}
{\bodytext{Helped in the evaluation of a class of around 75 students by marking formal oral presentations, midterm and final examinations for the \textit{Communication Skills: Oral/Written} mid-undergraduate course introducing concepts associated with technical writing and presentation.}}

\headedsubsection
{Learning Centre Staff, Faculty of Computer Science}{2012 -- 2013}
{\bodytext{Worked as a tutor at set hours in a faculty help facility for any Computer Science or Informatics undergraduate-level course. Supervised by Prof. \href{nauzerk@cs.dal.ca}{Nauzer Kalyaniwalla}.}}

\headedsubsection
{Research Assistant, Prof. \href{mailto:Mary.Anne.White@dal.ca}{Mary Anne White}}{Apr '10 -- Sep '10}
{\bodytext{Worked as a summer research assistant in the Department of Chemistry for a group focused on physical chemistry of materials, and helped write a journal article for the Ashrae 2011 Annual Conference on Solar Panels and the use of Phase Change Materials (PCMs) to store energy. A prototype was helped built for this manner of application for a local facility.}}

\headedsubsection
{Research Assistant, Prof. \href{mailto:peter.wentzell@dal.ca}{Peter Wentzell}}{Apr '09 -- Sep '09}
{\bodytext{Worked as a summer research assistant in the Department of Chemistry for a group focused on chemometrics and the analysis of chemical data, and helped write a suite of software that helped in the finding of genetic motifs in DNA sequences and to evaluate statistical plots of findings.}}

}

\headedsection{Cove Market \& Video}
{\textsc{Halifax, Canada}} {

\headedsubsection
{Sales Clerk}
{Sep '04 -- Sep '08}
{\bodytext{Convenience store sales, stocking, and general aide.}}
}

\begin{center}
\textit{Please refer to \href{http://ca.linkedin.com/in/asafatli}{my Linkedin profile} for further details and any relevant recommendations.}
\end{center}

\spacedhrule{-0.2em}{-0.4em} % <hr />

%----------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------

\roottitle{Publications}

\nocite{Latent2012}
\nocite{DCSI2012}
\nocite{Ref2013}
\nocite{Lisbon2015}
\printbibliography[heading=none]

\spacedhrule{0.5em}{-0.4em} % <hr />

%----------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------

\roottitle{Awards \& Achievements}


\headedsection{Natural Sci. \& Eng. Research Council (NSERC)}{\textsc{Canada}}{

\headedsubsection
{Undergraduate Student Research Award}{Jan '13, Jan '12, Jan '09}
{\bodytext{Procured funding for the working in a computer science laboratory during the summer term on the merit of grades and indication of interests. Awarded at three different occasions.}}}

\spacedhrule{0.5em}{-0.4em} % <hr />

%----------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------

\roottitle{Skills}

\inlineheadsection
{Technical Specialties}
{Software design and implementation, with(in) a team. Scientific writing. Advanced experience with Python/Java/C/C++/\LaTeX and regularly work with Objective-C, C\# (.NET framework), and Perl. Elementary to intermediate knowledge with Go, Scala, Lua, Prolog, Haskell, Scheme, Matlab, and R. Solid knowledge of database technologies: My\acr{SQL}, \acr{SQL}ite, No\acr{SQL}. Solid knowledge of web technologies:\ \acr{HTML+CSS}, \acr{XML}, \acr{REST}, JavaScript (jQuery, D3). Linux administration skills:\ bash, Apache, My\acr{SQL}, \acr{VM}ware.}

\inlineheadsection 
{Methodologies}
{Have worked with different tools of machine learning including support vector machine (SVM) and random forests. Have also done a large deal of information extraction, data classification, data visualization, and data mining using conventional and classical tools.}

\inlineheadsection 
{Natural Languages}
{English \textit{(mother tongue)}, Arabic \textit{(limited working proficiency)}, and French \textit{(elementary proficiency)}.}

%------------------------------------------------

\spacedhrule{1.6em}{-0.4em} % <hr />

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\roottitle{Interests} % Top level section

\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Non-exhaustive and in alphabetical order:}
{Art, cryptography, gaming, music, open source, philosophy, software engineering, typography (e.g.\ graphic design, \LaTeX).}

%------------------------------------------------

\spacedhrule{1.6em}{-0.4em} % <hr />

%----------------------------------------------------------------------------------------
%	OPEN SOURCE SECTION
%----------------------------------------------------------------------------------------

\roottitle{Open Source Project Contributions} % Top level section

\inlineheadsection{Minor Contributions:}
{\href{http://www.chromium.org}{Chromium Browser}.}

%------------------------------------------------

\end{document}