% Cies Resume/CV Template
% cies@kde.nl [https://github.com/cies/resume]

\documentclass[10pt,a4paper]{article}
\include{structure}
\addbibresource{publications}
\hyphenation{Phylogenetic}

% Name/Contact Information
\begin{document} 
\maintitle{Alexander Safatli}{July 13, 1990}

\noindent\href{mailto:safatli@cs.dal.ca}{safatli@cs.dal.ca}\bull
\textsmaller{+}1 (902) 229-0408\bull \textbf{GitHub} \href{https://github.com/AlexSafatli/}{AlexSafatli}\bull
\textbf{LinkedIn} \href{http://ca.linkedin.com/in/asafatli}{asafatli}\bull \textbf{Web} \href{http://alexsafatli.me}{alexsafatli.me}\\
100 Birch Tree Ln, B3R 2N8\bull Halifax, Nova Scotia\bull Canada
\spacedhrule{0.9em}{-0.4em} % <hr />

% Summary
\roottitle{Summary}
\vspace{-1.3em}
\begin{multicols}{2}
\noindent \textit{Recent graduate of a Master of Computer Science thesis program at Dalhousie University. Software developer with a reputation for rigorous thinking and methodological consistency. Looking to start my career in the private sector.}

I aspire to learn, design, build, and explore complex computer models. I promise to approach any tasks with an open mind and strong discipline, to be open to criticism and to consider new ideas, and to be someone you can trust to adapt and perform to new situations and technologies.
\end{multicols}
\spacedhrule{0.5em}{-0.4em} % <hr />

% Education
\roottitle{Education}
\headedsection{Dalhousie University}{\textsc{Halifax, Canada}} {
\headedsubsection{Master of Computer Science}{2014 -- 2015}
{\bodytext{\begin{itemize}\item Education in Adv.\ Data Structures, Algorithms, Heuristics, and Natural Language Processing. \item Published and currently maintain a Python software framework for combinatorial space analysis. \end{itemize}\textit{Supervised} by Assoc.\ Prof.\ \href{mailto:cblouin@cs.dal.ca}{Christian Blouin}. \textit{Extracurricular}. Computer Science Graduate Society, Executive Secretary for later term of 2014.}}

\headedsubsection{Bachelor of Computer Science with Distinction \bull GPA 3.8 \bull Dean's List}{2008 -- 2013}
{\bodytext{\begin{itemize} \item Thorough breadth of computer science fundamentals without specialization. \item Further focus on mathematics (geometry, cryptography, linear algebra) alongside chemistry. \item Completed individual and collaborative software projects in Java incl. a geo-location mobile game.\end{itemize} \textit{Awards}. Undergraduate Student Research Award from NSERC for summer internships in 2009, 2012, and 2013. \textit{Extracurricular}. Computer Science Society, Dalhousie University, Executive Secretary as of 2012-2013.}}}

\spacedhrule{0.5em}{-0.4em} % <hr />

%----------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------

\roottitle{Experience}

\headedsection{Dalhousie University}{\textsc{Halifax, Canada}}{

\headedsubsection
{Teaching Assistant}{2012 -- 2015}
{\bodytext{\textsc{Operating Systems} -- Winter 2015. Marked software assignments written in C. \textsc{Principles of Programming Languages} -- Summer 2014. Marked software assignments written in Scheme and Prolog. \textsc{Concepts in Computing}, \textsc{Bioinformatics} -- various terms 2012-2014. Marked written and programming assignments covering a breadth of topics in computer science and bioinformatics. \textsc{Comm.\ Skills: Oral/Written} -- various terms 2012-2013. Marked, help teach oral presentations and common business document writing. \textit{References}.\ Assist.\ Prof.\ \href{mailto:mcallist@cs.dal.ca}{Michael McAllister}, Prof.\ \href{mailto:pcox@cs.dal.ca}{Philip T. Cox}, Assoc.\ Prof.\ \href{mailto:cblouin@cs.dal.ca}{Christian Blouin}, Instr.\ \href{mailto:jfleming@cs.dal.ca}{James Fleming}.}}

\headedsubsection
{Research Assistant \& Software Developer, \href{http://web.cs.dal.ca/~cblouin/}{Blouin Lab}}
{2012 -- 2014}
{\bodytext{Took major part in writing Python libraries for geometric morphometric analysis of 2D and 3D biological structures, for molecular dynamics, for protein homology modelling, and for the parsing of essential file formats. These software libraries are used regularly by other graduate students in the laboratory for their projects. \textit{Reference}. Assoc.\ Prof.\ \href{mailto:cblouin@cs.dal.ca}{Christian Blouin}.}}}

\begin{center}
\textit{Please refer to \href{http://ca.linkedin.com/in/asafatli}{my Linkedin profile} for further experience and any relevant recommendations.}
\end{center}

\spacedhrule{-0.2em}{-0.4em} % <hr />

%----------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------

\roottitle{Skills}

\inlineheadsection
{Technical Knowledge}
{Software design and implementation, with(in) a team. Technical/scientific writing and use of the \LaTeX\ typesetting engine. Adv.\ experience with Python, Java, C, Objective-C, and Perl. Elementary to intermediate knowledge with C++, C\# (.NET framework), Go, Scala, Lua, Prolog, Haskell, Scheme, Matlab, and R. Knowledge of database technologies: My\acr{SQL}, \acr{SQL}ite, No\acr{SQL}. Knowledge of web technologies:\ \acr{HTML+CSS}, \acr{XML}, \acr{REST}, \acr{JSON}, JavaScript (jQuery, D3).}

\inlineheadsection 
{Natural Languages}
{English \textit{(mother tongue)}, Arabic \textit{(limited working proficiency)}, and French \textit{(elementary proficiency)}.}

%------------------------------------------------

\spacedhrule{1.6em}{-0.4em} % <hr />

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\roottitle{Interests} % Top level section

\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Non-exhaustive and in alphabetical order:}
{Art, cryptography, gaming, guitar, music (collecting, recording), open source, philosophy, reading, typography.}

%------------------------------------------------


\end{document}
