% Cies Resume/CV Template
% cies@kde.nl [https://github.com/cies/resume]

\documentclass[10pt,a4paper]{article}
\include{structure}
\hyphenation{Phylogenetic}

% Name/Contact Information
\begin{document} 
\maintitle{Alexander Safatli}{}

\noindent\href{mailto:safatli@cs.dal.ca}{safatli@cs.dal.ca}\bull
\textsmaller{+}1 (902) 229-0408\bull \textbf{GitHub} \href{https://github.com/AlexSafatli/}{AlexSafatli}\bull
\textbf{LinkedIn} \href{http://ca.linkedin.com/in/asafatli}{asafatli}\bull \textbf{Web} \href{http://alexsafatli.me}{alexsafatli.me}\\
100 Birch Tree Ln, B3R 2N8\bull Halifax, Nova Scotia\bull Canada
\spacedhrule{0.9em}{-0.4em} % <hr />

%----------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------

\roottitle{Experience}

\headedsection{Watzan, LLC}{\textsc{Halifax, Canada}}{
  
  \vspace{4pt}
  \headedsubsection{Software Developer}{June 2015 -- Present}
  {\vspace{4pt} \bodytext{One of a small number of developers that are constructing and managing an MVC architecture that uses social media information from hundreds of users to tailor content and search results. Software work is done using a mixture of Ruby on Rails, Coffeescript, and HTML.}}

}

\headedsection{Dalhousie University}{\textsc{Halifax, Canada}}{

\vspace{4pt}

\headedsubsection
{Teaching Assistant}{2012 -- 2015}
{\vspace{4pt} \bodytext{\begin{itemize} \setlength{\itemsep}{3pt} \item \textsc{Operating Systems} -- Winter 2015. Marked software assignments written in C. \item \textsc{Principles of Programming Languages} -- Summer 2014. Marked Scheme and Prolog assignments. \item \textsc{Concepts in Computing}, \textsc{Bioinformatics} -- various terms 2012-2014. Marked written and programming assignments covering a breadth of topics in computer science and bioinformatics. \item \textsc{Comm.\ Skills: Oral/Written} -- various terms 2012-2013. Marked, help teach oral presentations and common business document writing. \end{itemize}}}

\vspace{4pt}

\headedsubsection
{Research Assistant \& Software Developer, \href{http://web.cs.dal.ca/~cblouin/}{Blouin Lab}}
{2012 -- 2014}
{\vspace{4pt} \bodytext{Took major part in writing Python libraries for geometric morphometric analysis of 2D and 3D biological structures, for molecular dynamics, for protein homology modelling, and for the parsing of essential file formats. These software libraries are used regularly by other graduate students in the laboratory for their projects.}}}

\begin{center}
\textit{Please refer to \href{http://ca.linkedin.com/in/asafatli}{my Linkedin profile} for further experience and any relevant recommendations.}
\end{center}

\spacedhrule{-0.2em}{-0.4em} % <hr />

% Education
\roottitle{Education}
\headedsection{Dalhousie University}{\textsc{Halifax, Canada}} {

\vspace{4pt}

\headedsubsection{Master of Computer Science}{2014 -- 2015}
{\vspace{4pt} \bodytext{\begin{itemize} \setlength{\itemsep}{3pt} \item Education in Adv.\ Data Structures, Algorithms, Heuristics, and Natural Language Processing. \item A full web application for visualization of large combinatorial space graphs was constructed. \item Published and maintain a Python software framework for combinatorial space analysis. \end{itemize} \vspace{4pt} \textit{Supervised} by Assoc.\ Prof.\ \href{mailto:cblouin@cs.dal.ca}{Christian Blouin}.}}

\vspace{4pt}

\headedsubsection{Bachelor of Computer Science with Distinction \bull GPA 3.8 (Major: 4.0) \bull Dean's List}{2008 -- 2013}
{\vspace{4pt} \bodytext{\begin{itemize} \setlength{\itemsep}{3pt} \item Thorough breadth of computer science fundamentals without specialization. \item Completed individual and collaborative software projects in Java.\end{itemize} \vspace{4pt} \textit{Awards}. Undergraduate Student Research Award from NSERC for summer internships in 2009, 2012, and 2013.}}}

\vspace{4pt}

\spacedhrule{0.5em}{-0.4em} % <hr />

%----------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------

\roottitle{Skills}

\headedsubsection
{Technical Knowledge}{}
{\vspace{4pt} \bodytext{\begin{itemize} \setlength{\itemsep}{3pt} \item Experience with technical writing and documentation, through teaching and as a researcher. \item Advanced experience with Python, Java, C, and Ruby. \item Elementary to intermediate knowledge with C++, C\# (.NET framework), Go, Ruby, PHP, Objective-C, Perl, and Prolog. \item Knowledge of \textbf{\textsc{database technologies}}: My\acr{SQL}, \acr{SQL}ite, No\acr{SQL}. \item Knowledge of \textbf{\textsc{web technologies}}:\ \acr{HTML+CSS}, \acr{XML}, \acr{REST}, \acr{JSON}, Ruby on Rails, JavaScript. \end{itemize}}}

\inlineheadsection 
{Natural Languages}
{English \textit{(mother tongue)} and French \textit{(elementary proficiency)}.}


\end{document}
