%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.5in,top=0.6in,right=0.5in,bottom=0.6in]{geometry} % Document margins

\name{Alexander Safatli} % Your name
\address{100 Birch Tree Lane \\ Halifax, NS, Canada B3R2N8} % Your address
\address{(902) 222-2084 \\ alex@safatli.dev} % Your phone number and email
\address{\textsc{GitHub} AlexSafatli \\ \textsc{LinkedIn} asafatli \\ \texttt{https://safatli.dev}} % Github, Linkedin, web

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Dalhousie University, Canada} \hfill {June 2015} \\ 
M.S.E. in Computer Science (GPA 4.3) \\
B.S.E. in Computer Science (In-major GPA 4.0) \smallskip \\
\textit{Coursework}. Algorithms, Data Structures, NLP, OS, DBs, Software Engineering, \\
Principles of Programming Languages, Architecture, Cryptography, Discrete Math \textit{et al.} \smallskip \\
\textit{Extracurricular}. Secretary of Computer Science Graduate Society, Computer Science Society

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Liberated Networks}{January 2019 - Present}{Software Developer}{Halifax, NS}
\item Maintenance of several ASP.NET applications contracted out to national ISPs. C\# and JavaScript.
\item Exploration of machine learning techniques when applied to resumes and job matching. Python.
\item Partial ownership of a Java Spring and Angular 7 stack that is used to collaborate on work tasks.
\end{rSubsection}

\begin{rSubsection}{BeyondTrust}{January 2017 - November 2017}{Software Engineer}{Halifax, NS}
\item Maintained full stack development of a cyber security software deployment suite packaged with software used by and marketed to Fortune 100 companies. Angular.js and Go.
\item Managed tooling for software deployment for the team via tools like Jenkins and Docker.  
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Amazon}{January 2016 - October 2016}{Software Development Engineer I}{Seattle, WA}
\item Touched both frontend and backend components of an established e-commerce platform.
\item Worked on a team focusing on payment methods and gift card redemption. Java, C++, Perl, and Python.
\item Served on-call a number of weeks on a regular monthly basis to monitor and manage large demand web services and platforms.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{1ex}} l }
Computer Languages & C, Go, Python, Java, Typescript, Ruby, C\#, C++, Lua, Prolog, Haskell, Scheme, R \\
Protocols \& APIs & XML, JSON, REST, IMAP, SMTP, POP3, HTTP, UDP, TCP \\
Frameworks & Ruby on Rails, Django, Flask, Angular, ASP.NET, Mason, Tensorflow \\ 
Databases & MySQL, PostgreSQL, Microsoft SQL, Mongo, Dynamo \\
Methodologies & Machine Learning (SVMs, Random Forests, DNNs, k-NN), Data Mining \\
Tools & Git, SVN, \LaTeX, Unix (ricing, GNU utilities, etc.), \texttt{bash}, \texttt{zsh}, \texttt{vim}, \texttt{emacs}
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}

\begin{description}
\item [Operating System (2014-2015)] UNIX-style x86 system with bare bone essentials. C and Assembly.
\item [\textit{Pylogeny} (2016)] Framework for combinatorics in phylogeny. Peer-reviewed and published in \textit{PeerJ}. Python.
\item [ABeRMuSA (2016)] CLI that performs multiple 3D protein structure alignment. Python.
\item [NootBot (2016-)] Discord bot that automates tasks and emulates a soundboard in $n$ servers. Java Spring.
\end{description}

\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
